Adapting Duplicate Filters to a Sliding Window Context

### 2020-03-03 qhtv2.tex
Cleanup, clarifications in defs

\author{Rémi Géraud-Stewart}
\affiliation{%
  \institution{Département d'informatique de l'ENS, école normale supérieure, CNRS, PSL Research University}
  \city{Paris}
  \state{France}
}
\email{remi.geraud@ens.fr}

\author{Marius Lombard-Platet}
\affiliation{%
  \institution{Département d'informatique de l'ENS, école normale supérieure, CNRS, PSL Research University}
  \city{Paris}
  \country{France}
}
\affiliation{%
\institution{Be-Studys}
\city{Geneva}
\country{Switzerland}
}
\email{marius.lombard-platet@ens.fr}

\author{David Naccache}
\affiliation{%
  \institution{Département d'informatique de l'ENS, école normale supérieure, CNRS, PSL Research University}
  \city{Paris}
  \country{France}
}
\email{david.naccache@ens.fr}

\begin{abstract}
We introduce a generic framework for adapting duplicate filters for sliding windows. Most papers on the literature focus on the fact that a filter must detect a duplicate on the whole stream. In this paper, we recall from previous work that this problem is ill-defined, and that

\todo 
\end{abstract}

%
% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}

\end{CCSXML}

\keywords{datasets, neural networks, gaze detection, text tagging}

@@

\section{Introduction}
\subsection{Motivation}
As the Internet has grown in popularity, data streams have become bigger and bigger. However, while the datasets grow, the need for a quick answer has remained the same. Yet, in many cases, it is not possible to find the optimal solution by storing all the data, may it be for time limitation or memory limitations. Hence, researchers have gone forward and proposed approximate algorithms, that thrive to get as close as possible to the solution, despite the lack of memory and CPU time.

Such algorithms are present in network management \cite{10.5555/647912.740658}, in credit card fraud \cite{DBLP:journals/corr/abs-1709-08920}, phone calls data mining \cite{10.1145/347090.347094} and many other topics. A discussion about algorithms on large data streams can be found in \cite{10.1145/776985.776986}.

In this paper, we focus on the topic of duplicate detection. While many authors in the literature tackle the problem of approximate duplicate detection with fuzzy matching, \cite{10.5555/1287369.1287420,1410199,10.1109/ICDE.2011.5767865,10.1109/ICDE.2012.20,Monge97anefficient}, we instead focus on \emph{exact} duplicate detection, in which an element is a duplicate if and only if it has already appeared in the stream. One can prove (see for instance \cite[][Theorem 2.1]{10.1145/3297280.3297335}) that perfect detection of duplicates over an alphabet of $U$ letters requires $U$ bits of memory. Yet, in the case of extremely large alphabets, it is not possible or desirable to use that amount of memory.

As it turns out, (exact) duplicate detection has many real-life use cases, and can sometimes play a critical role, for instance in cryptographic schemes where all security and secrecy fall apart as soon as a random nonce is used twice, such as the Elgamal scheme \cite{10.1007/3-540-39568-7_2}. Other uses include improvements over caches \cite{4484874}, duplicate clicks \cite{10.1145/1060745.1060753}, and others.

@@

\section{Duplicate Detection and Filter Saturation}
\subsection{Notations and Initial Problem Statement}
Let us consider an alphabet $\Gamma$ of $U$ elements. A stream $E$ of $n$ elements of $\Gamma$ is noted $E = \{e_1, \dotsc, e_n\}$. If the stream is infinite or of unknown size, we note $E = \{e_1, \dotsc, e_n, \dotsc\}$.

\begin{definition}[Duplicate element, unseen element]
Let $E = \{e_1, \dotsc, e_n, \dotsc\}$ be a stream over $\Gamma$. $e_j$ is called a \emph{duplicate} in $E$ if and only if $\exists i < j, e_i = e_j$. Otherwise, $e_j$ is said to be \emph{unseen}.
\end{definition}

A filter $\mathcal F$ is defined by $\mathcal F = (\mathcal S, \mathsf{Insert}, \mathsf{Detect})$. Furthermore,

\begin{itemize}
	\item $\mathcal S \in \mathcal M$ represents the current state of the filter amongst all possible memory states $\mathcal M$.
	\item $\mathsf{Detect}: \mathcal M \times \Gamma \rightarrow \{\DUPLICATE, \UNSEEN\}$ is an algorithm that given the current state $\mathcal S$, guesses if an element $e$ is a duplicate or not.
	\item $\mathsf{Insert}: \mathcal M \times \Gamma \rightarrow \mathcal M$ takes as input the current state, an element $e$ to insert in the filter, and returns an updated memory state.
\end{itemize}

Furthermore, since we work in a context where the memory is too small for perfect detection, we have the assumption that $|\mathsf S| \ll U$.

\begin{definition}[False positive, false negative]
	Let $e$ be an unseen (resp. duplicate) element in the stream $E = \{e_1, \dotsc, e_n\}$, and let $\mathcal F$ be a filter. $e$ is a \emph{false positive} (resp. \emph{false negative}) if $\mathsf{Detect}(e) = \DUPLICATE$ (resp. $\UNSEEN$).
\end{definition}

\begin{definition}[False positive rate, false negative rate]
	Let $E = \{e_1, \dotsc, e_n\}$ be a stream, $\mathcal F$ be a filter. The false positive (resp. false negative) rate of $\mathcal F$ over the first $i < n$ elements, noted $\FPR_i$ (resp. $\FNR_i$), is defined as the number of false positives divided by the number of unseen elements of $\{e_1, \dotsc, e_i\}$ (resp. the number of false negative divided by the number of duplicate elements).
\end{definition}

@@

%\begin{acks}
%
%\end{acks}

%
% The next two lines define the bibliography style to be used, and the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-base}

% 
% If your work has an appendix, this is the place to put it.
%\appendix

%\section{Research Methods}

>>>>

%% Replace by \iffalse when submitting anonymously 
\iftrue 
	\author{Rémi Géraud-Stewart}
	\affiliation{%
	\institution{Département d'informatique de l'ENS, École normale supérieure, CNRS, PSL Research University}
	\city{Paris} \state{France}
	} \email{remi.geraud@ens.fr}

	\author{Marius Lombard-Platet}
	\affiliation{%
	\institution{Département d'informatique de l'ENS, École normale supérieure, CNRS, PSL Research University}
	\city{Paris} \country{France}
	}
	\affiliation{%
	\institution{Be-Studys}
	\city{Geneva} \country{Switzerland}
	} \email{marius.lombard-platet@ens.fr}

	\author{David Naccache}
	\affiliation{%
	\institution{Département d'informatique de l'ENS, École normale supérieure, CNRS, PSL Research University}
	\city{Paris} \country{France}
	} \email{david.naccache@ens.fr}
\fi

%% Abstract
\begin{abstract}
	A duplicate filter is a data structure designed to efficiently detect repetitions (duplicates) in a stream. A well-known instance of such a data structure is the Bloom filter, which has been generalised in several ways.

	In this paper we introduce a generic framework that adapts duplicate filters to sliding windows, rather than on an infinite stream. Indeed, although the
	infinite stream setting is known to be ill-defined, many duplicate filters are only described in such a scenario. This enables a rigourous mathematical study of such filters.
\end{abstract}

%% CCS XML
\begin{CCSXML}
	% Get code at http://dl.acm.org/ccs.cfm.
	% Please copy and paste the code
\end{CCSXML}

%% Keywords
\keywords{
	% TODO
}

@@

\section{Introduction}
\subsection{Motivation}

\paragraph{Duplicate detection problem.}
We consider the following problem (duplicate detection problem, DPP): given a stream $S_t = \{s_t, s_{t-1}, \dotsc\}$ and an item $s^\star$, find whether $s^\star \in S_t$. It is understood that the stream $S_t$ is updated at every time increment. An \emph{efficient} solution to this problem provides an answer with bounded error $\epsilon$, using polynomially many resources (time and memory) in $1/epsilon$.

Instances of this problem abound in computer science, with applications in file system indexation, database queries, network load balancing, network management \cite{10.5555/647912.740658}, in credit card fraud \cite{DBLP:journals/corr/abs-1709-08920}, phone calls data mining \cite{10.1145/347090.347094}, etc. A discussion about algorithms on large data streams can be found in \cite{10.1145/776985.776986}. 
Even when the stream is bounded, i.e. $\lim_{t\to\infty}|S_t| < \infty$, it may be impractical to perform a complete lookup and approximate solutions are desirable.

\paragraph{Approximate and exact DPP.}
One way to relax the DPP is to allow \emph{approximate} duplicate detection \cite{10.5555/1287369.1287420,1410199,10.1109/ICDE.2011.5767865,10.1109/ICDE.2012.20,Monge97anefficient}. We instead focus on \emph{exact} duplicate detection, in which an element is considered a duplicate if and only if it has already appeared in the stream. One can prove \cite[Theorem 2.1]{10.1145/3297280.3297335} that perfect detection of duplicates over an alphabet of $U$ letters requires $U$ bits of memory.

As it turns out, exact duplicate detection has many real-life use cases, and can sometimes play a critical role, for instance in cryptographic schemes where all security and secrecy fall apart as soon as a random nonce is used twice, such as the ElGamal \cite{10.1007/3-540-39568-7_2} or ECDSA signatures. Other uses include improvements over caches \cite{4484874}, duplicate clicks \cite{10.1145/1060745.1060753}, and others.

@@

\section{Duplicate Detection and Filter Saturation}
\subsection{Notations and Initial Problem Statement}
Let us consider an alphabet $\Gamma$. A stream $E$ over $\Gamma$ is a (possibly infinite) collection $E = \{e_1, e_2, \dotsc\}$, with each $e_i \in \Gamma$.

\begin{definition}[Duplicate and unseen element]
Let $E = \{e_i\}$ be a stream over $\Gamma$. Some element $e_j \in E$ is called a \emph{duplicate} if and only if there exists $i < j$ such that $e_i = e_j$. Otherwise, $e_j$ is said to be \emph{unseen}.
\end{definition}

\begin{definition}[Duplace detection filter]
	A \emph{duplicate detection filter} (DDF) is a collection of two algorithms 
	$\mathcal F = (\mathcal S, \mathsf{Insert}, \mathsf{Detect})$ of a state $\mathcal S \in \mathcal M$\footnote{Here, $\mathcal M$ denotes all the memory states that can be reached by the filter.} and two algorithms,
	\begin{itemize}
		\item $\mathsf{Detect}: \mathcal M \times \Gamma \to \{\DUPLICATE, \UNSEEN\}$;
		\item $\mathsf{Insert}: \mathcal M \times \Gamma \to \mathcal M$.
	\end{itemize}
	Informally, the $\mathsf{Detect}$ algorithm tentatively labels an element $e$ as duplicate or not, given the current state $\mathcal S$; whereas $\mathsf{Insert}$ takes as input the current state, an element $e$ to insert in the filter, and returns an updated memory state $\mathcal S'$. 
\end{definition}

We will usually consider the situations where the available memory is too small for perfect detection, i.e., $|\mathsf S| \ll |\Gamma|$.

\begin{definition}[False positive, false negative]
	Let $e \in E$ be an unseen (resp. duplicate) and $\mathcal F$ be a filter. We say that $e$ is a \emph{false positive} (resp. \emph{false negative}) when $\mathcal F.\mathsf{Detect}(e) = \DUPLICATE$ (resp. $\UNSEEN$).
\end{definition}

\begin{definition}[False positive rate, false negative rate]
	Let $E$ be a stream, $\mathcal F$ be a filter. The \emph{false positive rate} (resp. \emph{false negative rate}) of $\mathcal F$ over the first $i < n$ elements, denoted $\FPR_i$ (resp. $\FNR_i$), is defined as the ratio of false positives divided over the number of unseen elements in $\{e_1, \dotsc, e_i\}\subset E$ (resp. the ratio of false negative divided by the number of duplicate elements in that subset).
\end{definition}

@@

%% Acknowledgements 
%\begin{acks} \end{acks}

%% Bibliography
\bibliographystyle{ACM-Reference-Format}
\bibliography{qhtv2.bib}

%% Appendix
%\appendix
